Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-05 minimax.tex
Started chng Limited

The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n+1$ candidate questions: one per agent, and one to the chair. Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative. The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}. Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$. As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second. An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives \commentOC{(with equal likelyhood?)}\commentBN{We are not asking questions yet. We select as a candidate question the one corresponding to the situation. If you mean "what if there are several alternatives that can be placed between the two?" then yes, we pick one equiprobably.}, hoping for an answer that would prevent the adversary to play his best game. If $x^{*}$ and $\bar{y}$ are incomparable, then the candidate question to agent $j$ simply consists in comparing the two alternatives.
To define the candidate question to the chair, consider
%\begin{align}
$\w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
%\end{align}
the weight vector that minimize the $\PMR$ in the worst case. \commentOC{Changed this.} Define the spread at rank $r$ as $\sum_{k \in \set{0, 1, 2}}\abs{\bar{\w}_{r + k} - \w^{\tau}_{r + k}}$. We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes the spread at $r$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
After having selected the candidate questions, we apply the Pessimistic strategy. We evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.

>>>>

The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n + m$ candidate questions: one per agent, and one per rank. Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative. The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}. Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$. As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second. An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives \commentOC{(with equal likelyhood?)}\commentBN{We are not asking questions yet. We select as a candidate question the one corresponding to the situation. If you mean "what if there are several alternatives that can be placed between the two?" then yes, we pick one equiprobably.}, hoping for an answer that would prevent the adversary to play his best game. If $x^{*}$ and $\bar{y}$ are incomparable, then the candidate question to agent $j$ simply consists in comparing the two alternatives.
To define the candidate question to the chair, consider
%\begin{align}
$\w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
%\end{align}
the weight vector that minimize the $\PMR$ in the worst case. \commentOC{Changed this.} Define the spread at rank $r$ as $\sum_{k \in \set{0, 1, 2}}\abs{\bar{\w}_{r + k} - \w^{\tau}_{r + k}}$. We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes the spread at $r$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
After having selected the candidate questions, we apply the Pessimistic strategy. We evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.
